Single-cell virus sequencing of influenza infections that trigger innate immunity

### 2018-10-06 paper/paper.tex
modest edits to shorten validation section of Results

One other interesting trend emerges from the single-cell data.
There is no difference in the amount of viral mRNA between IFN+ and IFN- cells that express NS---but among cells that lack NS, the IFN+ ones have significantly more viral mRNA (\FIG{mutations}D).
The statistical analysis in \FIG{mutations}D is insufficient to determine if the higher viral transcriptional burden in IFN+ NS-deficient infections is a cause or a consequence of IFN induction, but experiments below shed more light on this question.

@@

We tested the rate of IFN induction by each viral stock using the reporter cells.
\FIG{validation} shows that five of the eight mutant viral stocks induced IFN more frequently than wild type.
The strongest IFN induction was by the NS1stop virus, but the PB1 internal deletion and three of the point-mutant viruses (PB1-D27N, PB1-T677A, and NS1-A122V) also induced IFN significantly more frequently than wild type.
Therefore, the viral defects in single IFN+ cells often cause increased IFN production.

It is tempting to compare the rates of IFN induction measured in \FIG{validation} with the enrichment of viral defects among the IFN+ cells in the single-cell data.
However, these comparisons are confounded by the fact that the measurements in \FIG{validation} use \emph{bulk} stocks of each viral mutant---and, as shown by the single-cell data in \FIG{genotypes}, many virions in each stock will also have additional mutations.
So although increased IFN induction by the mutant viral stocks does indicate the mutations are causally associated with IFN, it is impossible to know how many of the IFN+ cells induced by each stock are infected by virions that also have other defects.
The rate of IFN induction by any given viral mutant can only be accurately quantified by single-cell virus-sequencing.

>>>>

One other interesting trend emerges from the single-cell data.
There is no difference in the amount of viral mRNA between IFN+ and IFN- cells that express NS---but among cells that lack NS, the IFN+ ones have significantly more viral mRNA (\FIG{mutations}D).

@@

We tested the rate of IFN induction by each viral stock using the reporter cells.
\FIG{validation} shows that five of the eight mutant viral stocks induced IFN more frequently than wild type.
The strongest IFN induction was by the NS1stop virus, but the PB1 internal deletion and three of the point-mutant viruses (PB1-D27N, PB1-T677A, and NS1-A122V) also induced IFN significantly more frequently than wild type.
The other three point mutants (PB1-G206S, PB1-K279R, and NS2-E47G) did not increase IFN induction---an unsurprising finding, since we also expect some mutations without an IFN-enhancing effect to be found in IFN+ cells by chance.
But overall, the results in \FIG{validation} validate that the viral defects in single IFN+ cells often cause increased IFN production.
